---
title: "Values from vaccine scenarios"
output:
  html_document: default
  pdf_document: default
date: "2025-06-27"
---

```{r orderly, include=FALSE}
orderly_pars <- orderly2::orderly_parameters(short_run = FALSE,
                             fit_by_age = TRUE,
                             deterministic = FALSE,
                             short_run = FALSE,
                             mixing_matrix = "Zimbabwe",
                             fit_KPs = TRUE, 
                             assumptions = "standard",
                             vaccines_onset = "start")
list2env(orderly_pars, environment())
library(tidyr)

# Load in all dependencies 
orderly2::orderly_dependency(
  name = "pmcmc",
  query = "latest(parameter:region=='sudkivu')",
  files = c("inputs/samples_sudkivu.rds" = "outputs/samples.rds",
            "inputs/fitting_data_sudkivu.rds" = "outputs/fitting_data.rds"))
orderly2::orderly_dependency(
  name = "pmcmc",
  query = "latest(parameter:region=='equateur')",
  files = c("inputs/samples_equateur.rds" = "outputs/samples.rds",
            "inputs/fitting_data_equateur.rds" = "outputs/fitting_data.rds"))
orderly2::orderly_dependency(
  name = "pmcmc_burundi", 
  query =  "latest()", 
  files = c("inputs/samples_burundi.rds" = "outputs/samples.rds",
            "inputs/fitting_data_burundi.rds" = "outputs/fitting_data.rds"))

orderly2::orderly_dependency(name = "run_postprocess",
                             "latest(parameter:region =='sudkivu' && 
                                     parameter:deterministic == FALSE && 
                                     parameter:use_both_fit == FALSE && 
                                     parameter:fit_by_age == TRUE && 
                                     parameter:fit_KPs == TRUE &&
                                     parameter:short_run == FALSE && 
                                     parameter:vaccines_onset == 'start')",
                             files=c("inputs/runs_postprocess_sudkivu.RDS" = "outputs/runs_postprocess.RDS"))
orderly2::orderly_dependency(name = "run_postprocess",
                             "latest(parameter:region =='equateur' && 
                                     parameter:deterministic == FALSE && 
                                     parameter:use_both_fit == FALSE && 
                                     parameter:fit_by_age == TRUE && 
                                     parameter:fit_KPs == TRUE &&
                                     parameter:short_run == FALSE && 
                                     parameter:vaccines_onset == 'start')",
                             files=c("inputs/runs_postprocess_equateur.RDS" = "outputs/runs_postprocess.RDS"))
orderly2::orderly_dependency(name = "run_postprocess_burundi",
                             "latest(parameter:deterministic == FALSE && 
                             parameter:short_run == FALSE)",
                             files=c("inputs/runs_postprocess_burundi.RDS" = "outputs/runs_postprocess.RDS"))
# Populations of provinces
province_pop<-mpoxseir::parameters_demographic(region="sudkivu")$province_pop


######## Colour Palettes ########

scenarios_palette_vaccine <- c("No vaccination" = "black",
                               "LC16m8" = "#75884BFF",
                               "LC16m8 & MVA-BN" = "#5B859EFF",
                               "One dose MVA-BN"= "#800000",
                               "Two doses MVA-BN"= "#B38711FF",
                               "One dose fractional MVA-BN" = "#D48F90FF")
#  #AB84A5FF"

# all scenario names A-F
scenario_names_plots <- c("A: LC16m8", 
                          "B: LC16m8 + kids first",
                          "C: LC16m8 & MVA-BN",
                          "D: LC16m8 & MVA-BN + kids first", 
                          "E: LC16m8 & MVA-BN + SWs first",
                          "F: MVA-BN", 
                          "G: MVA-BN + kids first", 
                          "H: MVA-BN + SWs first",
                          "I: MVA-BN + fractional",
                          "J: MVA-BN + fractional + kids first",
                          "K: MVA-BN + fractional + SWs first",
                          "L: Two dose MVA-BN"
                          )

# line type
linetype_priority <- c("All equal"="solid",
                       "<12 years first"="dashed",
                       "SWs first"="dotted")
# shape
shape_priority <- c("All equal"=4,
                    "<12 years first"=16,
                    "SWs first"=17)


cols_region <- c(MetBrewer::met.brewer("Cassatt1", 7)[c(5,1)],MetBrewer::met.brewer("Demuth", 3)[3], MetBrewer::met.brewer("Cassatt1", 7)[3]) 
names(cols_region) <- c("equateur", "sudkivu", "both", "burundi")
nms_region <- c(equateur = "Equateur", sudkivu = "Sud Kivu", burundi = "Burundi")

# Dates 
vaccines_onset = "start"
start_date<-mpoxseir::mpoxseir_date_as_date(371) #+ 14

library(tidyverse)

orderly2::orderly_resource("support.R")
source("support.R")
orderly2::orderly_shared_resource("calc-Rt.R")
source("calc-Rt.R")

```



```{r setup, include=FALSE}
region <-"equateur"

# load in post process
big_df_equateur_start <-  readRDS("inputs/runs_postprocess_equateur.RDS") |> 
  mutate(Date = start_date + lubridate::days((TimeStep-1) * 7)) |> 
  mutate(scenario_combo=scenario_name, scenario_name=sub(" \\(.*", "", scenario_new), 
         scenario_dose=total_doses_children+total_doses_adults,
         scenario_labels= case_when(
           # LC16m8 to everyone
           scenario_new=="LC16m8" ~ "A: LC16m8",
           scenario_new=="LC16m8 + kids first" ~ "B: LC16m8 + kids first",
           # LC16m8 to uner 12s & one dose MVA-BN to over 12s
           scenario_new=="LC16m8 + MVA-BN >12y" ~ "C: LC16m8 & MVA-BN",
           scenario_new=="LC16m8 + MVA-BN >12y + kids first" ~ "D: LC16m8 & MVA-BN + kids first",
           scenario_new=="LC16m8 + MVA-BN >12y + SWs first" ~ "E: LC16m8 & MVA-BN + SWs first",
           # One dose MVA-BN to everyone
           scenario_new=="MVA-BN + 1st dose only" ~ "F: MVA-BN",
           scenario_new=="MVA-BN + 1st dose only + kids first" ~ "G: MVA-BN + kids first",
           scenario_new=="MVA-BN  + 1st dose only + SWs first" ~ "H: MVA-BN + SWs first",
           scenario_new=="MVA-BN + fractional" ~ "I: MVA-BN + fractional",
           scenario_new=="MVA-BN + fractional + kids first" ~ "J: MVA-BN + fractional + kids first",
           scenario_new=="MVA-BN + fractional + SWs first" ~ "K: MVA-BN + fractional + SWs first",
           # Two doses of MVA-BN to everyone
           scenario_new=="MVA-BN" ~ "L: Two dose MVA-BN",
           scenario_new=="MVA-BN + kids first" ~ "M: Two dose MVA-BN + kids first",
           scenario_new=="MVA-BN + SWs first" ~ "N: Two dose MVA-BN + SWs first"
         ),
         scenario_vaccine= case_when(
           # LC16m8 to everyone
           scenario_new=="LC16m8" ~ "LC16m8",
           scenario_new=="LC16m8 + kids first" ~ "LC16m8",
           # LC16m8 to uner 12s & one dose MVA-BN to over 12s
           scenario_new=="LC16m8 + MVA-BN >12y" ~ "LC16m8 & MVA-BN",
           scenario_new=="LC16m8 + MVA-BN >12y + kids first" ~ "LC16m8 & MVA-BN",
           scenario_new=="LC16m8 + MVA-BN >12y + SWs first" ~ "LC16m8 & MVA-BN",
           # One dose MVA-BN to everyone
           scenario_new=="MVA-BN + 1st dose only" ~ "One dose MVA-BN",
           scenario_new=="MVA-BN + 1st dose only + kids first" ~ "One dose MVA-BN",
           scenario_new=="MVA-BN  + 1st dose only + SWs first" ~ "One dose MVA-BN",
           scenario_new=="MVA-BN + fractional" ~ "One dose fractional MVA-BN",
           scenario_new=="MVA-BN + fractional + kids first" ~ "One dose fractional MVA-BN",
           scenario_new=="MVA-BN + fractional + SWs first" ~ "One dose fractional MVA-BN",
           # Two doses of MVA-BN to everyone
           scenario_new=="MVA-BN" ~ "Two doses MVA-BN",
           scenario_new=="MVA-BN + kids first" ~ "Two doses MVA-BN",
           scenario_new=="MVA-BN + SWs first" ~ "Two doses MVA-BN"
         ),
         scenario_priority= case_when(
           # LC16m8 to everyone
           scenario_new=="LC16m8" ~ "All equal",
           scenario_new=="LC16m8 + kids first" ~ "<12 years first",
           # LC16m8 to uner 12s & one dose MVA-BN to over 12s
           scenario_new=="LC16m8 + MVA-BN >12y" ~ "All equal",
           scenario_new=="LC16m8 + MVA-BN >12y + kids first" ~ "<12 years first",
           scenario_new=="LC16m8 + MVA-BN >12y + SWs first" ~ "SWs first",
           # One dose MVA-BN to everyone
           scenario_new=="MVA-BN + 1st dose only" ~ "All equal",
           scenario_new=="MVA-BN + 1st dose only + kids first" ~ "<12 years first",
           scenario_new=="MVA-BN  + 1st dose only + SWs first" ~ "SWs first",
           scenario_new=="MVA-BN + fractional" ~ "All equal",
           scenario_new=="MVA-BN + fractional + kids first" ~ "<12 years first",
           scenario_new=="MVA-BN + fractional + SWs first" ~ "SWs first",
           # Two doses of MVA-BN to everyone
           scenario_new=="MVA-BN" ~ "All equal",
           scenario_new=="MVA-BN + kids first" ~ "<12 years first",
           scenario_new=="MVA-BN + SWs first" ~ "SWs first"
         ),
        
         ) %>%
  mutate(
    scenario_dose_all = scenario_dose,
    scenario_dose = case_when(
    scenario_new=="MVA-BN + fractional" ~ scenario_dose/5,
    scenario_new=="MVA-BN + fractional + kids first" ~ scenario_dose/5,
    scenario_new=="MVA-BN + fractional + SWs first" ~ scenario_dose/5,
    .default=scenario_dose
  )) |>
  mutate(scenario_priority = factor(scenario_priority,
                                    levels=c("All equal","<12 years first",
                                             "SWs first")))|>
  mutate(scenario_doses_per_day_character=factor(format(scenario_doses_per_day_total, big.mark = ",", scientific = FALSE),
                                                 levels=c("   250","   500"," 1,000",
                                                          " 2,500"," 5,000","10,000", "20,000")))




# Plot max dose scenario
big_df_eq <- filter(big_df_equateur_start,
                          scenario_labels%in%scenario_names_plots[1:length(scenario_names_plots)])

# Region colour pallette
# load in fitting data
fitting_data_equateur <-  readRDS("inputs/fitting_data_equateur.RDS")


# Sud Kivu data
region <-"sudkivu"

# load in post process
big_df_sudkivu_start <-  readRDS("inputs/runs_postprocess_sudkivu.RDS") |> 
  mutate(Date = start_date + lubridate::days((TimeStep-1) * 7)) |> 
  mutate(scenario_combo=scenario_name, scenario_name=sub(" \\(.*", "", scenario_new), 
         scenario_dose=total_doses_children+total_doses_adults,
         scenario_labels= case_when(
           # LC16m8 to everyone
           scenario_new=="LC16m8" ~ "A: LC16m8",
           scenario_new=="LC16m8 + kids first" ~ "B: LC16m8 + kids first",
           # LC16m8 to uner 12s & one dose MVA-BN to over 12s
           scenario_new=="LC16m8 + MVA-BN >12y" ~ "C: LC16m8 & MVA-BN",
           scenario_new=="LC16m8 + MVA-BN >12y + kids first" ~ "D: LC16m8 & MVA-BN + kids first",
           scenario_new=="LC16m8 + MVA-BN >12y + SWs first" ~ "E: LC16m8 & MVA-BN + SWs first",
           # One dose MVA-BN to everyone
           scenario_new=="MVA-BN + 1st dose only" ~ "F: MVA-BN",
           scenario_new=="MVA-BN + 1st dose only + kids first" ~ "G: MVA-BN + kids first",
           scenario_new=="MVA-BN + 1st dose only + SWs first" ~ "H: MVA-BN + SWs first",
           scenario_new=="MVA-BN + fractional" ~ "I: MVA-BN + fractional",
           scenario_new=="MVA-BN + fractional + kids first" ~ "J: MVA-BN + fractional + kids first",
           scenario_new=="MVA-BN + fractional + SWs first" ~ "K: MVA-BN + fractional + SWs first",
           # Two doses of MVA-BN to everyone
           scenario_new=="MVA-BN" ~ "L: Two dose MVA-BN",
           scenario_new=="MVA-BN + kids first" ~ "M: Two dose MVA-BN + kids first",
           scenario_new=="MVA-BN + SWs first" ~ "N: Two dose MVA-BN + SWs first"
         ),
         scenario_vaccine= case_when(
           # LC16m8 to everyone
           scenario_new=="LC16m8" ~ "LC16m8",
           scenario_new=="LC16m8 + kids first" ~ "LC16m8",
           # LC16m8 to uner 12s & one dose MVA-BN to over 12s
           scenario_new=="LC16m8 + MVA-BN >12y" ~ "LC16m8 & MVA-BN",
           scenario_new=="LC16m8 + MVA-BN >12y + kids first" ~ "LC16m8 & MVA-BN",
           scenario_new=="LC16m8 + MVA-BN >12y + SWs first" ~ "LC16m8 & MVA-BN",
           # One dose MVA-BN to everyone
           scenario_new=="MVA-BN + 1st dose only" ~ "One dose MVA-BN",
           scenario_new=="MVA-BN + 1st dose only + kids first" ~ "One dose MVA-BN",
           scenario_new=="MVA-BN + 1st dose only + SWs first" ~ "One dose MVA-BN",
           scenario_new=="MVA-BN + fractional" ~ "One dose fractional MVA-BN",
           scenario_new=="MVA-BN + fractional + kids first" ~ "One dose fractional MVA-BN",
           scenario_new=="MVA-BN + fractional + SWs first" ~ "One dose fractional MVA-BN",
           # Two doses of MVA-BN to everyone
           scenario_new=="MVA-BN" ~ "Two doses MVA-BN",
           scenario_new=="MVA-BN + kids first" ~ "Two doses MVA-BN",
           scenario_new=="MVA-BN + SWs first" ~ "Two doses MVA-BN"
         ),
         scenario_priority= case_when(
           # LC16m8 to everyone
           scenario_new=="LC16m8" ~ "All equal",
           scenario_new=="LC16m8 + kids first" ~ "<12 years first",
           # LC16m8 to uner 12s & one dose MVA-BN to over 12s
           scenario_new=="LC16m8 + MVA-BN >12y" ~ "All equal",
           scenario_new=="LC16m8 + MVA-BN >12y + kids first" ~ "<12 years first",
           scenario_new=="LC16m8 + MVA-BN >12y + SWs first" ~ "SWs first",
           # One dose MVA-BN to everyone
           scenario_new=="MVA-BN + 1st dose only" ~ "All equal",
           scenario_new=="MVA-BN + 1st dose only + kids first" ~ "<12 years first",
           scenario_new=="MVA-BN + 1st dose only + SWs first" ~ "SWs first",
           scenario_new=="MVA-BN + fractional" ~ "All equal",
           scenario_new=="MVA-BN + fractional + kids first" ~ "<12 years first",
           scenario_new=="MVA-BN + fractional + SWs first" ~ "SWs first",
           # Two doses of MVA-BN to everyone
           scenario_new=="MVA-BN" ~ "All equal",
           scenario_new=="MVA-BN + kids first" ~ "<12 years first",
           scenario_new=="MVA-BN + SWs first" ~ "SWs first"
         ),
         
  ) |>
  mutate(
    scenario_dose_all = scenario_dose,
    scenario_dose = case_when(
      scenario_new=="MVA-BN + fractional" ~ scenario_dose/5,
      scenario_new=="MVA-BN + fractional + kids first" ~ scenario_dose/5,
      scenario_new=="MVA-BN + fractional + SWs first" ~ scenario_dose/5,
      .default=scenario_dose
    )) |>
  mutate(scenario_priority = factor(scenario_priority,
                                    levels=c("All equal","<12 years first",
                                             "SWs first")))|>
  mutate(scenario_doses_per_day_character=factor(format(scenario_doses_per_day_total, big.mark = ",", scientific = FALSE),
                                                 levels=c("   250","   500"," 1,000",
                                                          " 2,500"," 5,000","10,000", "20,000")))


# Plot max dose scenario
big_df_sk <- filter(big_df_sudkivu_start,
                          scenario_labels%in%scenario_names_plots[1:length(scenario_names_plots)])


# load in fitting data 
fitting_data_sudkivu <-  readRDS("inputs/fitting_data_sudkivu.RDS")


### Bujumbura data 
region <- "bujumbura"

## Fitting outputs
fitting_data_bujumbura <- readRDS("inputs/fitting_data_burundi.rds")


# load in post process

# load in post process
big_df_bujumbura_start <-  readRDS("inputs/runs_postprocess_burundi.RDS") |> 
  mutate(Date = start_date + lubridate::days((TimeStep-1) * 7)) |> 
  mutate(scenario_combo=scenario_name, scenario_name=sub(" \\(.*", "", scenario_new), 
         scenario_dose=total_doses_children+total_doses_adults,
         scenario_labels= case_when(
           # LC16m8 to everyone
           scenario_new=="LC16m8" ~ "A: LC16m8",
           scenario_new=="LC16m8 + kids first" ~ "B: LC16m8 + kids first",
           # LC16m8 to uner 12s & one dose MVA-BN to over 12s
           scenario_new=="LC16m8 + MVA-BN >12y" ~ "C: LC16m8 & MVA-BN",
           scenario_new=="LC16m8 + MVA-BN >12y + kids first" ~ "D: LC16m8 & MVA-BN + kids first",
           scenario_new=="LC16m8 + MVA-BN >12y + SWs first" ~ "E: LC16m8 & MVA-BN + SWs first",
           # One dose MVA-BN to everyone
           scenario_new=="MVA-BN + 1st dose only" ~ "F: MVA-BN",
           scenario_new=="MVA-BN + 1st dose only + kids first" ~ "G: MVA-BN + kids first",
           scenario_new=="MVA-BN + 1st dose only + SWs first" ~ "H: MVA-BN + SWs first",
           scenario_new=="MVA-BN + fractional" ~ "I: MVA-BN + fractional",
           scenario_new=="MVA-BN + fractional + kids first" ~ "J: MVA-BN + fractional + kids first",
           scenario_new=="MVA-BN + fractional + SWs first" ~ "K: MVA-BN + fractional + SWs first",
           # Two doses of MVA-BN to everyone
           scenario_new=="MVA-BN" ~ "L: Two dose MVA-BN",
           scenario_new=="MVA-BN + kids first" ~ "M: Two dose MVA-BN + kids first",
           scenario_new=="MVA-BN + SWs first" ~ "N: Two dose MVA-BN + SWs first"
         ),
         scenario_vaccine= case_when(
           # LC16m8 to everyone
           scenario_new=="LC16m8" ~ "LC16m8",
           scenario_new=="LC16m8 + kids first" ~ "LC16m8",
           # LC16m8 to uner 12s & one dose MVA-BN to over 12s
           scenario_new=="LC16m8 + MVA-BN >12y" ~ "LC16m8 & MVA-BN",
           scenario_new=="LC16m8 + MVA-BN >12y + kids first" ~ "LC16m8 & MVA-BN",
           scenario_new=="LC16m8 + MVA-BN >12y + SWs first" ~ "LC16m8 & MVA-BN",
           # One dose MVA-BN to everyone
           scenario_new=="MVA-BN + 1st dose only" ~ "One dose MVA-BN",
           scenario_new=="MVA-BN + 1st dose only + kids first" ~ "One dose MVA-BN",
           scenario_new=="MVA-BN + 1st dose only + SWs first" ~ "One dose MVA-BN",
           scenario_new=="MVA-BN + fractional" ~ "One dose fractional MVA-BN",
           scenario_new=="MVA-BN + fractional + kids first" ~ "One dose fractional MVA-BN",
           scenario_new=="MVA-BN + fractional + SWs first" ~ "One dose fractional MVA-BN",
           # Two doses of MVA-BN to everyone
           scenario_new=="MVA-BN" ~ "Two doses MVA-BN",
           scenario_new=="MVA-BN + kids first" ~ "Two doses MVA-BN",
           scenario_new=="MVA-BN + SWs first" ~ "Two doses MVA-BN"
         ),
         scenario_priority= case_when(
           # LC16m8 to everyone
           scenario_new=="LC16m8" ~ "All equal",
           scenario_new=="LC16m8 + kids first" ~ "<12 years first",
           # LC16m8 to uner 12s & one dose MVA-BN to over 12s
           scenario_new=="LC16m8 + MVA-BN >12y" ~ "All equal",
           scenario_new=="LC16m8 + MVA-BN >12y + kids first" ~ "<12 years first",
           scenario_new=="LC16m8 + MVA-BN >12y + SWs first" ~ "SWs first",
           # One dose MVA-BN to everyone
           scenario_new=="MVA-BN + 1st dose only" ~ "All equal",
           scenario_new=="MVA-BN + 1st dose only + kids first" ~ "<12 years first",
           scenario_new=="MVA-BN + 1st dose only + SWs first" ~ "SWs first",
           scenario_new=="MVA-BN + fractional" ~ "All equal",
           scenario_new=="MVA-BN + fractional + kids first" ~ "<12 years first",
           scenario_new=="MVA-BN + fractional + SWs first" ~ "SWs first",
           # Two doses of MVA-BN to everyone
           scenario_new=="MVA-BN" ~ "All equal",
           scenario_new=="MVA-BN + kids first" ~ "<12 years first",
           scenario_new=="MVA-BN + SWs first" ~ "SWs first"
         ),
         
  ) |>
  mutate(
    scenario_dose_all = scenario_dose,
    scenario_dose = case_when(
      scenario_new=="MVA-BN + fractional" ~ scenario_dose/5,
      scenario_new=="MVA-BN + fractional + kids first" ~ scenario_dose/5,
      scenario_new=="MVA-BN + fractional + SWs first" ~ scenario_dose/5,
      .default=scenario_dose
    )) |>
  mutate(scenario_priority = factor(scenario_priority,
                                    levels=c("All equal","<12 years first",
                                             "SWs first")))%>%
  mutate(scenario_doses_per_day_character=factor(format(scenario_doses_per_day_total, big.mark = ",", scientific = FALSE),
                                                 levels=c("   25","   50","  100","  250","  500","1,000", "2,000")))



# Plot max dose scenario
big_df_bu <- filter(big_df_bujumbura_start,
                          scenario_labels%in%scenario_names_plots[1:length(scenario_names_plots)])



```




## All regions: total infections/deaths averted - max dose/ middle dose per day/ best priority


```{r total percent, echo=FALSE, warning=FALSE, message=FALSE}
equateur_max_cases <- filter(big_df_equateur_start, 
                           scenario_labels=="B: LC16m8 + kids first",
                           scenario_dose==520000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("cases_inc_cum"))

sudkivu_max_cases<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c(
                            "K: MVA-BN + fractional + SWs first",
                             "H: MVA-BN + SWs first"),
                          scenario_dose==2000000,
                          scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))

bujumbura_max_cases<-filter(big_df_bujumbura_start, 
                            scenario_dose==50000,
                            scenario_doses_per_day_character == "  500",
                            scenario_labels%in%c("K: MVA-BN + fractional + SWs first","H: MVA-BN + SWs first"),
                            TimeStep==max(big_df_bujumbura_start$TimeStep, na.rm = TRUE), 
                            Category%in%c("cases_inc_cum"))
 # total cases averted 
total_cases_averted<-equateur_max_cases$mean_averted+
  sudkivu_max_cases$mean_averted+
  bujumbura_max_cases$mean_averted
# total baseline cases
total_cases_no_vaccine<-equateur_max_cases$mean_counter+
  sudkivu_max_cases$mean_counter+
  bujumbura_max_cases$mean_counter
# percentage of cases averted
print("Total percentage of cases averted:")
(total_cases_averted/total_cases_no_vaccine)*100

print("Eqauteur percentage of cases averted:")
equateur_max_cases$mean_percent*100
equateur_max_cases$lower_95_percent*100
equateur_max_cases$upper_95_percent*100

print("Sud Kivu percentage of cases averted:")
sudkivu_max_cases$mean_percent*100
sudkivu_max_cases$lower_95_percent*100
sudkivu_max_cases$upper_95_percent*100

print("Bujumbura percentage of cases averted:")
bujumbura_max_cases$mean_percent*100
bujumbura_max_cases$lower_95_percent*100
bujumbura_max_cases$upper_95_percent*100


equateur_max_deaths<-filter(big_df_equateur_start, 
                            scenario_doses_per_day_character == " 5,000",
                           scenario_labels=="B: LC16m8 + kids first",
                           scenario_dose==520000,
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("deaths_inc_cum"))

sudkivu_max_deaths<-filter(big_df_sudkivu_start, 
                            scenario_doses_per_day_character == " 5,000",
                          scenario_labels%in%c("K: MVA-BN + fractional + SWs first","H: MVA-BN + SWs first"),
                          scenario_dose==2000000,
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("deaths_inc_cum"))

bujumbura_max_extended<-filter(big_df_bujumbura_start, 
                            scenario_doses_per_day_character == "  500",
                            scenario_dose==800000,
                            scenario_labels%in%c("K: MVA-BN + fractional + SWs first","H: MVA-BN + SWs first"),
                            TimeStep==max(big_df_bujumbura_start$TimeStep, na.rm = TRUE), 
                            Category%in%c("cases_inc_cum"))
 
# total deaths averted 
total_deaths_averted<-equateur_max_deaths$mean_averted+
  sudkivu_max_deaths$mean_averted
# total deaths no vaccine
total_deaths_no_vaccine<-equateur_max_deaths$mean_counter+
  sudkivu_max_deaths$mean_counter
# percentage of deaths averted
print("Total percentage of deaths averted:")
(total_deaths_averted/total_deaths_no_vaccine)*100

print("Eqauteur percentage of deaths averted:")
equateur_max_deaths$mean_percent*100
equateur_max_deaths$lower_95_percent*100
equateur_max_deaths$upper_95_percent*100

print("Sud Kivu percentage of deaths averted:")
sudkivu_max_deaths$mean_percent*100
sudkivu_max_deaths$lower_95_percent*100
sudkivu_max_deaths$upper_95_percent*100

print("Bujumbura percentage of infection averted (extended analysis):")
bujumbura_max_extended$mean_percent*100
bujumbura_max_extended$lower_95_percent*100
bujumbura_max_extended$upper_95_percent*100


```


## Percent of SW & PBS infected by peak epidemic

# Sud Kivu 

```{r infections set up, include = FALSE}
# Equateur 
# read in scenario grid 
orderly2::orderly_shared_resource(DRC_scenario_grid.csv = "DRC_scenario_grid.csv") 
scenario_grid <- read_csv("DRC_scenario_grid.csv")|>filter(region=="equateur")

# Extracting scenario information and simulation output 
scenario_id <- scenario_num <- which(scenario_grid$scenario_name=="No vaccination")

file_name <- paste0("model_run_output_",scenario_num,"eq.rds")
  
     # Extracting all parameters from each scenario  
  n_weeks <- 104
  total_doses_children <- scenario_grid$total_doses_children[scenario_id]
  total_doses_adults<- scenario_grid$total_doses_adults[scenario_id]
  doses_per_day_total <- scenario_grid$doses_per_day_total[scenario_id] 
  daily_vax_split_children <- scenario_grid$daily_vax_split_children[scenario_id] 
  vaccine_dose_scenario <- scenario_grid$vaccine_dose_scenario[scenario_id]
  days_between_doses <- scenario_grid$days_between_doses[scenario_id]
  prioritisation_children <- scenario_grid$prioritisation_children[scenario_id]
  prioritisation_adults <- scenario_grid$prioritisation_adults[scenario_id]
  uptake_realised <- scenario_grid$uptake_realised[scenario_id]
  vaccine_used<- scenario_grid$vaccine_used[scenario_id]  

  orderly2::orderly_dependency(
    "run_scenario",
    quote(latest(  parameter:region == "equateur" &&
                     parameter:total_doses_adults == environment:total_doses_adults && 
                     parameter:total_doses_children == environment:total_doses_children && 
                     parameter:doses_per_day_total == environment:doses_per_day_total &&
                     parameter:daily_vax_split_children == environment:daily_vax_split_children &&
                     parameter:vaccine_dose_scenario == environment:vaccine_dose_scenario &&
                     parameter:days_between_doses == environment:days_between_doses &&
                     parameter:prioritisation_children == environment:prioritisation_children &&
                     parameter:prioritisation_adults == environment:prioritisation_adults &&
                     parameter:uptake_realised == environment:uptake_realised &&
                     parameter:scenario_num == environment:scenario_num &&
                     parameter:vaccines_onset == environment:vaccines_onset &&
                     parameter:vaccine_used == environment:vaccine_used)),
    files=c("inputs/${file_name}" = paste0("outputs/model_run_output_",scenario_num,".rds")))
  
  orderly2::orderly_dependency(
  name = "pmcmc",
  query = "latest(parameter:region=='sudkivu')",
  files = c("inputs/samples_sudkivu.rds" = "outputs/samples.rds",
            "inputs/fitting_data_sudkivu.rds" = "outputs/fitting_data.rds"))

  
  

  
  
# Sud Kivu
# mean peak date for no vaccine scenario 
SW_peak_mean <- filter(big_df_sudkivu_start, Category%in%c("cases_inc"))
peak_date<-SW_peak_mean$TimeStep[which(SW_peak_mean$mean_counter==max(SW_peak_mean$mean_counter))][1]
# date of peak - Sud Kivu
SW_peak_mean$date[which(SW_peak_mean$mean_counter==max(SW_peak_mean$mean_counter))][1]

# read in scenario grid 
orderly2::orderly_shared_resource(DRC_scenario_grid.csv = "DRC_scenario_grid.csv") 
scenario_grid <- read_csv("DRC_scenario_grid.csv")|>filter(region=="sudkivu")

# Extracting scenario information and simulation output 
scenario_id <- scenario_num <- which(scenario_grid$scenario_name=="No vaccination")
file_name <- paste0("model_run_output_",scenario_num,"sk.rds")

  
     # Extracting all parameters from each scenario  
  n_weeks <- 104
  total_doses_children <- scenario_grid$total_doses_children[scenario_id]
  total_doses_adults<- scenario_grid$total_doses_adults[scenario_id]
  doses_per_day_total <- scenario_grid$doses_per_day_total[scenario_id] 
  daily_vax_split_children <- scenario_grid$daily_vax_split_children[scenario_id] 
  vaccine_dose_scenario <- scenario_grid$vaccine_dose_scenario[scenario_id]
  days_between_doses <- scenario_grid$days_between_doses[scenario_id]
  prioritisation_children <- scenario_grid$prioritisation_children[scenario_id]
  prioritisation_adults <- scenario_grid$prioritisation_adults[scenario_id]
  uptake_realised <- scenario_grid$uptake_realised[scenario_id]
  vaccine_used<- scenario_grid$vaccine_used[scenario_id]  

  orderly2::orderly_dependency(
    "run_scenario",
    quote(latest(  parameter:region == "sudkivu" &&
                     parameter:total_doses_adults == environment:total_doses_adults && 
                     parameter:total_doses_children == environment:total_doses_children && 
                     parameter:doses_per_day_total == environment:doses_per_day_total &&
                     parameter:daily_vax_split_children == environment:daily_vax_split_children &&
                     parameter:vaccine_dose_scenario == environment:vaccine_dose_scenario &&
                     parameter:days_between_doses == environment:days_between_doses &&
                     parameter:prioritisation_children == environment:prioritisation_children &&
                     parameter:prioritisation_adults == environment:prioritisation_adults &&
                     parameter:uptake_realised == environment:uptake_realised &&
                     parameter:scenario_num == environment:scenario_num &&
                     parameter:vaccines_onset == environment:vaccines_onset &&
                     parameter:vaccine_used == environment:vaccine_used)),
    files=c("inputs/${file_name}" = paste0("outputs/model_run_output_",scenario_num,".rds")))
  


```



```{r Sud kivu percentage, echo=FALSE, warning=FALSE, message=FALSE}
# PMCMC output
pmcmc_results_s <- readRDS("inputs/samples_sudkivu.RDS")
fitting_data_s <- readRDS("inputs/fitting_data_sudkivu.RDS")
pars_tidy_s <- tidy_pars(pmcmc_results_s)
pars_unpacked_s <- apply(pmcmc_results_s$pars, 2, pmcmc_results_s$packer$unpack)

# Population data
pop_size <- mpoxseir::parameters_demographic(region="sudkivu")$province_pop

eqauteur_pop_prop <- pop_size$equateur/sum(mpoxseir::parameters_demographic(region="sudkivu")$N_age)
sudkivu_pop_prop <- pop_size$sudkivu/sum(mpoxseir::parameters_demographic(region="sudkivu")$N_age)

# Pmcmc output
SW_population<-pars_tidy_s|>filter(name=="prop_SW")|>mutate(population = pop_size$sudkivu,
                                                            eligible_pop = sum(mpoxseir::parameters_demographic(region="sudkivu")$N_age[3:10]*sudkivu_pop_prop),
                              # PBS population - from appendix
                              pop_pbs = 123113)|>
 # SW population
   mutate(pop_sw = ifelse(name=="prop_SW", value * eligible_pop, NA))
# Add Particle number]
SW_population<- SW_population|>mutate(Particle=1:nrow(SW_population))


# Scenario outputs
counter_output_sk <- readRDS(paste0("inputs/model_run_output_",scenario_id,"sk.rds")) %>%
  rename(counter =Value)
  
SW_peak_comp <- counter_output_sk |> filter(TimeStep%in%c(1:peak_date), Category%in%c("cases_inc_SW", "cases_inc_PBS"))

# SWs infected 
infected <- SW_peak_comp |> group_by(Particle, Category) |> summarise(counter=sum(counter)) |> pivot_wider(names_from = Category, values_from = counter)

# calculate percentages 
infected_precent <- full_join(infected, SW_population, by = "Particle")|>
  mutate(pbs_percent = cases_inc_PBS/pop_pbs, sw_percent = cases_inc_SW/pop_sw)

# summaraise mean and upper and lower 95% credible intervals 
infected_precent_summary <- infected_precent |> ungroup()|> summarise(pbs_percent_mean = mean(pbs_percent),
                                                          pbs_percent_median = median(pbs_percent), 
                                                          pbs_percent_lower_95_value = quantile(pbs_percent, 0.025, na.rm = TRUE),
                                                          pbs_percent_upper_95_value = quantile(pbs_percent, 0.975, na.rm = TRUE),
                                                          sw_percent_mean = mean(sw_percent),
                                                          sw_percent_median = median(sw_percent), 
                                                          sw_percent_lower_95_value = quantile(sw_percent, 0.025, na.rm = TRUE),
                                                          sw_percent_upper_95_value = quantile(sw_percent, 0.975, na.rm = TRUE),
                                                          sw_pop_mean = mean(pop_sw),
                                                          sw_pop_median = median(pop_sw), 
                                                          sw_pop_lower_95_value = quantile(pop_sw, 0.025, na.rm = TRUE),
                                                          sw_pop_upper_95_value = quantile(pop_sw, 0.975, na.rm = TRUE))


print("Mean percent of SWs at peak Sud Kivu:")
infected_precent_summary$sw_percent_mean*100
print("95% CrI:")
paste0("[",infected_precent_summary$sw_percent_lower_95_value*100,", ",
       infected_precent_summary$sw_percent_upper_95_value*100,"]")

print("Mean percent of PBSs at peak Sud Kivu:")
infected_precent_summary$pbs_percent_mean*100
print("95% CrI:")
paste0("[",infected_precent_summary$pbs_percent_lower_95_value*100,", ",
       infected_precent_summary$pbs_percent_upper_95_value*100,"]")

print("Mean SW popuation Sud Kivu:")
infected_precent_summary$sw_pop_mean
print("95% CrI:")
paste0("[",infected_precent_summary$sw_pop_lower_95_value,", ",
       infected_precent_summary$sw_pop_upper_95_value,"]")


## percentage of pop infected at start of outbreak


```


# Bujumbura 

```{r Bujumbura infections set up, include = FALSE}

# mean peak date for no vaccine scenario 
SW_peak_mean_bu <- filter(big_df_bujumbura_start, Category%in%c("cases_inc"))
peak_date_bu<-SW_peak_mean_bu$TimeStep[which(SW_peak_mean_bu$mean_counter==max(SW_peak_mean_bu$mean_counter))][1]
# date of peak - Bujumbura
SW_peak_mean_bu$date[which(SW_peak_mean_bu$mean_counter==max(SW_peak_mean_bu$mean_counter))][1]

# read in scenario grid 
orderly2::orderly_shared_resource(scenario_grid_burundi.RDS = "scenario_grid_burundi.RDS") 
scenario_grid_burundi <- readRDS("scenario_grid_burundi.RDS")

# Extracting scenario information and simulation output 
scenario_id_bu <- scenario_num <- scenario_grid_burundi$scenario_num[which(scenario_grid_burundi$vaccine_dose_scenario=="no_vaccine")]
file_name <- paste0("model_run_output_",scenario_id_bu,"bu.rds")
  
 # Extracting all parameters from each scenario  
  n_weeks <- 72
  total_doses_children <- scenario_grid_burundi$total_doses_children[scenario_id_bu]
  total_doses_adults<- scenario_grid_burundi$total_doses_adults[scenario_id_bu]
  doses_per_day_total <- scenario_grid_burundi$doses_per_day_total[scenario_id_bu] 
  daily_vax_split_children <- scenario_grid_burundi$daily_vax_split_children[scenario_id_bu] 
  vaccine_dose_scenario <- scenario_grid_burundi$vaccine_dose_scenario[scenario_id_bu]
  days_between_doses <- scenario_grid_burundi$days_between_doses[scenario_id_bu]
  prioritisation_children <- scenario_grid_burundi$prioritisation_children[scenario_id_bu]
  prioritisation_adults <- scenario_grid_burundi$prioritisation_adults[scenario_id_bu]
  uptake_realised <- scenario_grid_burundi$uptake_realised[scenario_id_bu]
  scenario_num <- scenario_grid_burundi$scenario_num[scenario_id_bu]         


  orderly2::orderly_dependency(
    "run_scenario_burundi",
    quote(latest( parameter:short_run == FALSE &&
                     parameter:fit_by_age == TRUE &&
                     parameter:deterministic == FALSE &&
                     parameter:fit_KPs== TRUE &&
                     parameter:total_doses_adults == environment:total_doses_adults && 
                     parameter:total_doses_children == environment:total_doses_children && 
                     parameter:doses_per_day_total == environment:doses_per_day_total &&
                     parameter:daily_vax_split_children == environment:daily_vax_split_children &&
                     parameter:vaccine_dose_scenario == environment:vaccine_dose_scenario &&
                     parameter:days_between_doses == environment:days_between_doses &&
                     parameter:prioritisation_adults == environment:prioritisation_adults &&
                     parameter:uptake_realised == environment:uptake_realised &&
                     parameter:vaccines_onset == environment:vaccines_onset &&
                     parameter:scenario_num == environment:scenario_num)),
    files=c("inputs/${file_name}" = paste0("outputs/model_run_output_",scenario_id_bu,".rds")))
  
  

```


```{r Bujumbura percentages, echo=FALSE, warning=FALSE, message=FALSE}
# PMCMC output
pmcmc_results_b <- readRDS("inputs/samples_burundi.RDS")
pars_tidy_b <- tidy_pars(pmcmc_results_b)
pars_unpacked_b <- apply(pmcmc_results_b$pars, 2, pmcmc_results_b$packer$unpack)

# Population data
pop_size <- mpoxseir::parameters_demographic(region="bujumbura")$province_pop
bujumbura_pop_prop<-pop_size$bujumbura/11890781
# Pmcmc output
SW_population_bu<-pars_tidy_b|>filter(name=="prop_SW")|>mutate(population = pop_size$bujumbura,
                                                            eligible_pop  = sum(mpoxseir::parameters_demographic(region="bujumbura")$N_age[3:10]*bujumbura_pop_prop),
                              # PBS population - from appendix
                              pop_pbs = 21870)|>
 # SW population
   mutate(pop_sw = ifelse(name=="prop_SW", value * eligible_pop, NA))
# Add Particle number]
SW_population_bu<- SW_population_bu|>mutate(Particle=1:nrow(SW_population))


# Scenario outputs
counter_output_bu <- readRDS(paste0("inputs/model_run_output_",scenario_id_bu,"bu.rds")) %>%
  rename(counter =Value)
  
SW_peak_comp_bu <- counter_output_bu |> filter(TimeStep%in%c(1:peak_date_bu), Category%in%c("cases_inc_PBS", "cases_inc_SW"))

# SWs infected 
infected_bu <- SW_peak_comp_bu |> group_by(Particle, Category) |> summarise(counter=sum(counter)) |> pivot_wider(names_from = Category, values_from = counter)

# calculate percentages 
infected_precent_bu <- full_join(infected_bu, SW_population_bu, by = "Particle")|>
  mutate(pbs_percent = cases_inc_PBS/pop_pbs, sw_percent = cases_inc_SW/pop_sw)

# summarise mean and upper and lower 95% credible intervals 
infected_precent_summary_bu <- infected_precent_bu |> ungroup()|> summarise(pbs_percent_mean = mean(pbs_percent),
                                                          pbs_percent_median = median(pbs_percent), 
                                                          pbs_percent_lower_95_value = quantile(pbs_percent, 0.025, na.rm = TRUE),
                                                          pbs_percent_upper_95_value = quantile(pbs_percent, 0.975, na.rm = TRUE),
                                                          sw_percent_mean = mean(sw_percent),
                                                          sw_percent_median = median(sw_percent), 
                                                          sw_percent_lower_95_value = quantile(sw_percent, 0.025, na.rm = TRUE),
                                                          sw_percent_upper_95_value = quantile(sw_percent, 0.975, na.rm = TRUE),
                                                          sw_pop_mean = mean(pop_sw),
                                                          sw_pop_median = median(pop_sw), 
                                                          sw_pop_lower_95_value = quantile(pop_sw, 0.025, na.rm = TRUE),
                                                          sw_pop_upper_95_value = quantile(pop_sw, 0.975, na.rm = TRUE))


print("Mean percent of SWs at peak Bujumbura:")
infected_precent_summary_bu$sw_percent_mean*100
print("95% CrI:")
paste0("[",infected_precent_summary_bu$sw_percent_lower_95_value*100,", ",infected_precent_summary_bu$sw_percent_upper_95_value*100,"]")

print("Mean percent of PBSs at peak Bujumbura:")
infected_precent_summary_bu$pbs_percent_mean*100
print("95% CrI:")
paste0("[",infected_precent_summary_bu$pbs_percent_lower_95_value*100,", ",infected_precent_summary_bu$pbs_percent_upper_95_value*100,"]")

print("Mean SW popuation Bujumbura:")
infected_precent_summary_bu$sw_pop_mean
print("95% CrI:")
paste0("[",infected_precent_summary_bu$sw_pop_lower_95_value,", ",
       infected_precent_summary_bu$sw_pop_upper_95_value,"]")

# percent of total infections that are SW?

#pars_unpacked_b[[1]]$N0
#pars_unpacked_b[[1]]$S0

```


# Percentage of population infected at start of data 


```{r infections outside percentages, echo=FALSE, warning=FALSE, message=FALSE}

# Bujumbura data starts on 595
pre_start<-big_df_bujumbura_start|>filter(Category%in%c("cases_inc"), date%in%(seq(from = mpoxseir::mpoxseir_date_as_date(490), to =mpoxseir::mpoxseir_date_as_date(594), by = "day")))
#sum(test$mean_counter)/pop_size$bujumbura
# 1 in X people:
print("Bujumbura, 1 in X people infected at start of data:")
pop_size$bujumbura/sum(pre_start$mean_counter)

# Sud Kivu data starts on 371
  samples <- readRDS("inputs/samples_sudkivu.rds")
    data <- readRDS("inputs/fitting_data_sudkivu.rds")

    trajectories <- apply(samples$observations$trajectories, c(1, 2), mean_ci)
    grid <- dimnames(trajectories)
    grid <- append(grid, values = region, after = 2)
    
    names(grid) <- c("name", "state", "region", "date")
  grid$date <- mpoxseir::mpoxseir_date_as_date(sort(unique(data$data$date)))
  fits <- expand.grid(grid)
  
  fits$value <- c(trajectories)
  fits_wide<-fits%>%pivot_wider(names_from = name, values_from = value)|>
    rename(Category=state, mean_counter=mean, lower_95_counter=q2.5, upper_95_counter=q97.5)
  
pre_start_sk<-fits_wide|>filter(Category%in%c("cases_inc"), date%in%(seq(from = mpoxseir::mpoxseir_date_as_date(280), to = mpoxseir::mpoxseir_date_as_date(370), by = "day")))
# 1 in X people:
print("Sud Kivu, 1 in X people infected at start of data:")
pop_size$sudkivu/sum(pre_start_sk$mean_counter)


```


## Scenario values
## Eqauteur, 520,000 doses/5,000 doses per day - LC16m8 + kids first

```{r eqauteur scenarios 1, echo=FALSE, warning=FALSE, message=FALSE }

equateur_best_scenario<-filter(big_df_equateur_start, 
                           scenario_labels=="B: LC16m8 + kids first",
                           scenario_dose==520000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("cases_inc_cum"))
print("Mean cases averted:")
equateur_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_averted, ", ", equateur_best_scenario$upper_95_averted, "]")


print("Mean percent cases averted:")
equateur_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_percent, ", ", equateur_best_scenario$upper_95_percent, "]")


print("Mean cases averted per dose:")
equateur_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_averted_95_per_dose, ", ", equateur_best_scenario$upper_averted_95_per_dose, "]")

# Deaths 
equateur_best_scenario_deaths<-filter(big_df_equateur_start, 
                           scenario_labels=="B: LC16m8 + kids first",
                           scenario_dose==520000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("deaths_inc_cum"))
print("Mean deaths averted:")
equateur_best_scenario_deaths$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_averted, ", ", equateur_best_scenario_deaths$upper_95_averted, "]")


print("Mean percent deaths averted:")
equateur_best_scenario_deaths$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_percent, ", ", equateur_best_scenario_deaths$upper_95_percent, "]")

```

## Eqauteur, 260,000 doses/5,000 doses per day - LC16m8 + kids first

```{r eqauteur scenarios 2, echo=FALSE, warning=FALSE, message=FALSE }

equateur_best_scenario<-filter(big_df_equateur_start, 
                           scenario_labels=="B: LC16m8 + kids first",
                           scenario_dose==260000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("cases_inc_cum"))
print("Mean cases averted:")
equateur_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_averted, ", ", equateur_best_scenario$upper_95_averted, "]")


print("Mean percent cases averted:")
equateur_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_percent, ", ", equateur_best_scenario$upper_95_percent, "]")


print("Mean cases averted per dose:")
equateur_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_averted_95_per_dose, ", ", equateur_best_scenario$upper_averted_95_per_dose, "]")

# Deaths 
equateur_best_scenario_deaths<-filter(big_df_equateur_start, 
                           scenario_labels=="B: LC16m8 + kids first",
                           scenario_dose==260000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("deaths_inc_cum"))
print("Mean deaths averted:")
equateur_best_scenario_deaths$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_averted, ", ", equateur_best_scenario_deaths$upper_95_averted, "]")


print("Mean percent deaths averted:")
equateur_best_scenario_deaths$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_percent, ", ", equateur_best_scenario_deaths$upper_95_percent, "]")

```

## Eqauteur, 260,000 doses/5,000 doses per day - LC16m8 + no priority

```{r eqauteur scenarios 3, echo=FALSE, warning=FALSE, message=FALSE }

equateur_best_scenario<-filter(big_df_equateur_start, 
                           scenario_labels=="A: LC16m8",
                           scenario_dose==260000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("cases_inc_cum"))
print("Mean cases averted:")
equateur_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_averted, ", ", equateur_best_scenario$upper_95_averted, "]")


print("Mean percent cases averted:")
equateur_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_percent, ", ", equateur_best_scenario$upper_95_percent, "]")


print("Mean cases averted per dose:")
equateur_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_averted_95_per_dose, ", ", equateur_best_scenario$upper_averted_95_per_dose, "]")

# Deaths 
equateur_best_scenario_deaths<-filter(big_df_equateur_start, 
                           scenario_labels=="A: LC16m8",
                           scenario_dose==260000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("deaths_inc_cum"))
print("Mean deaths averted:")
equateur_best_scenario_deaths$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_averted, ", ", equateur_best_scenario_deaths$upper_95_averted, "]")


print("Mean percent deaths averted:")
equateur_best_scenario_deaths$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_percent, ", ", equateur_best_scenario_deaths$upper_95_percent, "]")

```

## Eqauteur, 520,000 doses/5,000 doses per day - one dose fractional MVA no priority

```{r eqauteur scenarios 1 dose fractional, echo=FALSE, warning=FALSE, message=FALSE }

equateur_best_scenario<-filter(big_df_equateur_start, 
                           scenario_labels=="I: MVA-BN + fractional",
                           scenario_dose==520000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("cases_inc_cum"))
print("Mean cases averted:")
equateur_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_averted, ", ", equateur_best_scenario$upper_95_averted, "]")


print("Mean percent cases averted:")
equateur_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_percent, ", ", equateur_best_scenario$upper_95_percent, "]")


print("Mean cases averted per dose:")
equateur_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_averted_95_per_dose, ", ", equateur_best_scenario$upper_averted_95_per_dose, "]")

# Deaths 
equateur_best_scenario_deaths<-filter(big_df_equateur_start, 
                           scenario_labels=="I: MVA-BN + fractional",
                           scenario_dose==520000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("deaths_inc_cum"))
print("Mean deaths averted:")
equateur_best_scenario_deaths$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_averted, ", ", equateur_best_scenario_deaths$upper_95_averted, "]")


print("Mean percent deaths averted:")
equateur_best_scenario_deaths$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_percent, ", ", equateur_best_scenario_deaths$upper_95_percent, "]")

```

## Eqauteur, 520,000 doses/5,000 doses per day - one dose MVA no priority

```{r eqauteur scenarios 1 dose, echo=FALSE, warning=FALSE, message=FALSE }

equateur_best_scenario<-filter(big_df_equateur_start, 
                           scenario_labels=="F: MVA-BN",
                           scenario_dose==520000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("cases_inc_cum"))
print("Mean cases averted:")
equateur_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_averted, ", ", equateur_best_scenario$upper_95_averted, "]")


print("Mean percent cases averted:")
equateur_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_percent, ", ", equateur_best_scenario$upper_95_percent, "]")


print("Mean cases averted per dose:")
equateur_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_averted_95_per_dose, ", ", equateur_best_scenario$upper_averted_95_per_dose, "]")

# Deaths 
equateur_best_scenario_deaths<-filter(big_df_equateur_start, 
                           scenario_labels=="F: MVA-BN",
                           scenario_dose==520000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("deaths_inc_cum"))
print("Mean deaths averted:")
equateur_best_scenario_deaths$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_averted, ", ", equateur_best_scenario_deaths$upper_95_averted, "]")


print("Mean percent deaths averted:")
equateur_best_scenario_deaths$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_percent, ", ", equateur_best_scenario_deaths$upper_95_percent, "]")

```


`
## Eqauteur, 520,000 doses/5,000 doses per day - two dose MVA no priority

```{r eqauteur scenarios 2 dose, echo=FALSE, warning=FALSE, message=FALSE }

equateur_best_scenario<-filter(big_df_equateur_start, 
                           scenario_labels=="L: Two dose MVA-BN",
                           scenario_dose==520000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("cases_inc_cum"))
print("Mean cases averted:")
equateur_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_averted, ", ", equateur_best_scenario$upper_95_averted, "]")


print("Mean percent cases averted:")
equateur_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_percent, ", ", equateur_best_scenario$upper_95_percent, "]")


print("Mean cases averted per dose:")
equateur_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_averted_95_per_dose, ", ", equateur_best_scenario$upper_averted_95_per_dose, "]")

# Deaths 
equateur_best_scenario_deaths<-filter(big_df_equateur_start, 
                           scenario_labels=="L: Two dose MVA-BN",
                           scenario_dose==520000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("deaths_inc_cum"))
print("Mean deaths averted:")
equateur_best_scenario_deaths$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_averted, ", ", equateur_best_scenario_deaths$upper_95_averted, "]")


print("Mean percent deaths averted:")
equateur_best_scenario_deaths$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario_deaths$lower_95_percent, ", ", equateur_best_scenario_deaths$upper_95_percent, "]")

```

## Eqauteur, 130,000 doses/5,000 doses per day - one and fractional dose MVA no priority

```{r eqauteur fractional, echo=FALSE, warning=FALSE, message=FALSE }

print("one full dose")
equateur_best_scenario<-filter(big_df_equateur_start, 
                           scenario_labels=="F: MVA-BN",
                           scenario_dose==130000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("cases_inc_cum"))
print("Mean cases averted:")
equateur_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_averted, ", ", equateur_best_scenario$upper_95_averted, "]")


print("Mean percent cases averted:")
equateur_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_percent, ", ", equateur_best_scenario$upper_95_percent, "]")


print("Mean cases averted per dose:")
equateur_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_averted_95_per_dose, ", ", equateur_best_scenario$upper_averted_95_per_dose, "]")



print("one fractional dose")
equateur_best_scenario<-filter(big_df_equateur_start, 
                           scenario_labels=="I: MVA-BN + fractional",
                           scenario_dose==130000,
                           scenario_doses_per_day_character == " 5,000",
                           TimeStep==max(big_df_equateur_start$TimeStep),
                           Category%in%c("cases_inc_cum"))
print("Mean cases averted:")
equateur_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_averted, ", ", equateur_best_scenario$upper_95_averted, "]")


print("Mean percent cases averted:")
equateur_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_95_percent, ", ", equateur_best_scenario$upper_95_percent, "]")


print("Mean cases averted per dose:")
equateur_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",equateur_best_scenario$lower_averted_95_per_dose, ", ", equateur_best_scenario$upper_averted_95_per_dose, "]")


```


## Sud Kivu, 2 million doses - MVA-BN single dose + SWs first + fractional

```{r sud kivu scenarios 1, echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_best_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("K: MVA-BN + fractional + SWs first"),
                          scenario_dose==2000000,
                           scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))

print("Mean cases averted:")
sudkivu_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_best_scenario$lower_95_averted, ", ", sudkivu_best_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_best_scenario$lower_95_percent, ", ", sudkivu_best_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_best_scenario$lower_averted_95_per_dose, ", ", sudkivu_best_scenario$upper_averted_95_per_dose, "]")


sudkivu_best_scenario_deaths<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("K: MVA-BN + fractional + SWs first"),
                          scenario_dose==2000000,
                           scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("deaths_inc_cum"))

print("Mean deaths averted:")
sudkivu_best_scenario_deaths$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_best_scenario_deaths$lower_95_averted, ", ", sudkivu_best_scenario_deaths$upper_95_averted, "]")

print("Mean percent deaths averted:")
sudkivu_best_scenario_deaths$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_best_scenario_deaths$lower_95_percent, ", ", sudkivu_best_scenario_deaths$upper_95_percent, "]")
```


## Sud Kivu, 10,000 doses/5,000 doses per day - MVA-BN single dose + SWs first 

```{r sud kivu scenarios 2, echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_10000_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("K: MVA-BN + fractional + SWs first",
                                               "H: MVA-BN + SWs first"),
                          scenario_dose==10000,
                          scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))

print("Mean cases averted:")
cbind(sudkivu_10000_scenario$scenario_labels,sudkivu_10000_scenario$mean_averted)
print("95% CrI interval:")
cbind(sudkivu_10000_scenario$scenario_labels,paste0("[",sudkivu_10000_scenario$lower_95_averted, ", ", sudkivu_10000_scenario$upper_95_averted, "]"))

print("Mean percent cases averted:")
cbind(sudkivu_10000_scenario$scenario_labels,sudkivu_10000_scenario$mean_percent)
print("95% CrI interval:")
cbind(sudkivu_10000_scenario$scenario_labels,paste0("[",sudkivu_10000_scenario$lower_95_percent, ", ", sudkivu_10000_scenario$upper_95_percent, "]"))

print("Mean cases averted per dose:")
cbind(sudkivu_10000_scenario$scenario_labels,sudkivu_10000_scenario$mean_averted_per_dose)
print("95% CrI interval:")
cbind(sudkivu_10000_scenario$scenario_labels,paste0("[",sudkivu_10000_scenario$lower_averted_95_per_dose, ", ", sudkivu_10000_scenario$upper_averted_95_per_dose, "]"))


sudkivu_10000_scenario_detahs<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("K: MVA-BN + fractional + SWs first",
                                               "H: MVA-BN + SWs first"),
                          scenario_dose==10000,
                           scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("deaths_inc_cum"))

print("Mean deaths averted:")
cbind(sudkivu_10000_scenario_detahs$scenario_labels,sudkivu_10000_scenario_detahs$mean_averted)
print("95% CrI interval:")
cbind(sudkivu_10000_scenario_detahs$scenario_labels,paste0("[",sudkivu_10000_scenario_detahs$lower_95_averted, ", ", sudkivu_10000_scenario_detahs$upper_95_averted, "]"))

print("Mean percent deaths averted:")
cbind(sudkivu_10000_scenario_detahs$scenario_labels,sudkivu_10000_scenario_detahs$mean_percent)
print("95% CrI interval:")
cbind(sudkivu_10000_scenario_detahs$scenario_labels,paste0("[",sudkivu_10000_scenario_detahs$lower_95_percent, ", ", sudkivu_10000_scenario_detahs$upper_95_percent, "]"))

```

## Sud Kivu, 10,000 doses/5,000 doses per day - MVA-BN single dose + no priority 

```{r sud kivu scenarios 2 no priority, echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_10000_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("F: MVA-BN", "I: MVA-BN + fractional"),
                          scenario_dose==10000,
                          scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))

print("Mean cases averted:")
sudkivu_10000_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_10000_scenario$lower_95_averted, ", ", sudkivu_10000_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_10000_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_10000_scenario$lower_95_percent, ", ", sudkivu_10000_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_10000_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_10000_scenario$lower_averted_95_per_dose, ", ", sudkivu_10000_scenario$upper_averted_95_per_dose, "]")


sudkivu_10000_scenario_detahs<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("H: MVA-BN + SWs first", "I: MVA-BN + fractional"),
                          scenario_dose==10000,
                           scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("deaths_inc_cum"))

print("Mean deaths averted:")
sudkivu_10000_scenario_detahs$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_10000_scenario_detahs$lower_95_averted, ", ", sudkivu_10000_scenario_detahs$upper_95_averted, "]")

print("Mean percent deaths averted:")
sudkivu_10000_scenario_detahs$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_10000_scenario_detahs$lower_95_percent, ", ", sudkivu_10000_scenario_detahs$upper_95_percent, "]")

```
## Sud Kivu, 1 million doses - MVA-BN single dose + kids first 

```{r sud kivu scenarios 1 mil, echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_best_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("G: MVA-BN + kids first"),
                          scenario_dose==1000000,
                           scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))

print("Mean cases averted:")
sudkivu_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_best_scenario$lower_95_averted, ", ", sudkivu_best_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_best_scenario$lower_95_percent, ", ", sudkivu_best_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_best_scenario$lower_averted_95_per_dose, ", ", sudkivu_best_scenario$upper_averted_95_per_dose, "]")


sudkivu_best_scenario_deaths<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("H: MVA-BN + SWs first"),
                          scenario_dose==2000000,
                           scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("deaths_inc_cum"))

print("Mean deaths averted:")
sudkivu_best_scenario_deaths$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_best_scenario_deaths$lower_95_averted, ", ", sudkivu_best_scenario_deaths$upper_95_averted, "]")
```


## Sud Kivu, 2 million doses - MVA-BN fractional single dose (no priority)

```{r sud kivu scenarios 3 frac , echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("F: MVA-BN",
                                               "I: MVA-BN + fractional"),
                          scenario_dose==2000000,
                          scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")
```

## Sud Kivu, 2 million doses - MVA-BN single dose (no priority)

```{r sud kivu scenarios 3 , echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("F: MVA-BN"),
                          scenario_dose==2000000,
                          scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")
```

## Sud Kivu, 2 million doses - MVA-BN two dose (no priority)

```{r sud kivu scenarios 5 , echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("L: Two dose MVA-BN"),
                          scenario_dose==2000000,
                          scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")
```


## Sud Kivu, 2 million doses - LC16m8 (no priority)

```{r sud kivu scenarios 4, echo=FALSE, warning=FALSE, message=FALSE }

sudkivu_lc16_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("A: LC16m8"),
                          scenario_dose==2000000,
                          scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))

print("Mean cases averted:")
sudkivu_lc16_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_lc16_scenario$lower_95_averted, ", ", sudkivu_lc16_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_lc16_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_lc16_scenario$lower_95_percent, ", ", sudkivu_lc16_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_lc16_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_lc16_scenario$lower_averted_95_per_dose, ", ", sudkivu_lc16_scenario$upper_averted_95_per_dose, "]")
```


##  Bujumbura, 50,000 doses/ 500 doses per day - MVA-BN single dose + SWs first
```{r bujumbura scenarios 1, echo=FALSE, warning=FALSE, message=FALSE}
bujumbura_best_scenario<-filter(big_df_bujumbura_start, 
                             scenario_dose==50000,
                             scenario_doses_per_day_character == "  500",
                            scenario_labels%in%c("H: MVA-BN + SWs first"),
                            TimeStep==max(big_df_bujumbura_start$TimeStep, na.rm = TRUE), 
                            Category%in%c("cases_inc_cum"))

print("Mean cases averted:")
bujumbura_best_scenario$mean_averted
print("95% CrI interval:")
paste0("[",bujumbura_best_scenario$lower_95_averted, ", ", bujumbura_best_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
bujumbura_best_scenario$mean_percent
print("95% CrI interval:")
paste0("[",bujumbura_best_scenario$lower_95_percent, ", ", bujumbura_best_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
bujumbura_best_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",bujumbura_best_scenario$lower_averted_95_per_dose, ", ", bujumbura_best_scenario$upper_averted_95_per_dose, "]")

```


##  Bujumbura, 800,000 doses/ 500 doses per day - MVA-BN single dose + SWs first/  MVA-BN two dose + SWs first
```{r bujumbura scenarios 2, echo=FALSE, warning=FALSE, message=FALSE}
bujumbura_best_scenario<-filter(big_df_bujumbura_start, 
                             scenario_dose==800000,
                             scenario_doses_per_day_character == "  500",
                            scenario_labels%in%c("I: MVA-BN + fractional",
                                                 "F: MVA-BN",
                                                 "K: MVA-BN + fractional + SWs first",
                                                 "L: Two dose MVA-BN"),
                            TimeStep==max(big_df_bujumbura_start$TimeStep, na.rm = TRUE), 
                            Category%in%c("cases_inc_cum"))

print("Mean cases averted:")
cbind(bujumbura_best_scenario$scenario_labels,bujumbura_best_scenario$mean_averted)
print("95% CrI interval:")
cbind(bujumbura_best_scenario$scenario_labels,
      paste0("[",bujumbura_best_scenario$lower_95_averted, ", ", bujumbura_best_scenario$upper_95_averted, "]"))

print("Mean percent cases averted:")
cbind(bujumbura_best_scenario$scenario_labels,bujumbura_best_scenario$mean_percent)
print("95% CrI interval:")
cbind(bujumbura_best_scenario$scenario_labels,paste0("[",bujumbura_best_scenario$lower_95_percent, ", ", bujumbura_best_scenario$upper_95_percent, "]"))

print("Mean cases averted per dose:")
cbind(bujumbura_best_scenario$scenario_labels,bujumbura_best_scenario$mean_averted_per_dose)
print("95% CrI interval:")
cbind(bujumbura_best_scenario$scenario_labels,paste0("[",bujumbura_best_scenario$lower_averted_95_per_dose, ", ", bujumbura_best_scenario$upper_averted_95_per_dose, "]"))

```


## rollout speed analysis 
# Bujumbura - 50,000 doses/ 25 doses per day/ all equal
```{r bujumbura scenarios rollout 1 all equal, echo=FALSE, warning=FALSE, message=FALSE}
bujumbura_25_scenario<-filter(big_df_bujumbura_start, 
                             scenario_dose==50000,
                             scenario_doses_per_day_character == "   25",
                            scenario_priority%in%c("All equal"),
                            TimeStep==max(big_df_bujumbura_start$TimeStep, na.rm = TRUE), 
                            Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
bujumbura_25_scenario$mean_averted
print("95% CrI interval:")
paste0("[",bujumbura_25_scenario$lower_95_averted, ", ", bujumbura_25_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
bujumbura_25_scenario$mean_percent
print("95% CrI interval:")
paste0("[",bujumbura_25_scenario$lower_95_percent, ", ", bujumbura_25_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
bujumbura_25_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",bujumbura_25_scenario$lower_averted_95_per_dose, ", ", bujumbura_25_scenario$upper_averted_95_per_dose, "]")

```

# Bujumbura - 50,000 doses/ 2,000 doses per day/ all equal
```{r bujumbura scenarios rollout 2 all equal, echo=FALSE, warning=FALSE, message=FALSE}
bujumbura_2000_scenario<-filter(big_df_bujumbura_start, 
                             scenario_dose==50000,
                             scenario_doses_per_day_character == "2,000",
                            scenario_priority%in%c("All equal"),
                            TimeStep==max(big_df_bujumbura_start$TimeStep, na.rm = TRUE), 
                            Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
bujumbura_2000_scenario$mean_averted
print("95% CrI interval:")
paste0("[",bujumbura_2000_scenario$lower_95_averted, ", ", bujumbura_2000_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
bujumbura_2000_scenario$mean_percent
print("95% CrI interval:")
paste0("[",bujumbura_2000_scenario$lower_95_percent, ", ", bujumbura_2000_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
bujumbura_2000_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",bujumbura_2000_scenario$lower_averted_95_per_dose, ", ", bujumbura_2000_scenario$upper_averted_95_per_dose, "]")

```

# Bujumbura - 50,000 doses/ 25 doses per day/ SW first
```{r bujumbura scenarios rollout 1 sw, echo=FALSE, warning=FALSE, message=FALSE}
bujumbura_25_scenario<-filter(big_df_bujumbura_start, 
                             scenario_dose==50000,
                             scenario_doses_per_day_character == "   25",
                            scenario_priority%in%c("SWs first"),
                            TimeStep==max(big_df_bujumbura_start$TimeStep, na.rm = TRUE), 
                            Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
bujumbura_25_scenario$mean_averted
print("95% CrI interval:")
paste0("[",bujumbura_25_scenario$lower_95_averted, ", ", bujumbura_25_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
bujumbura_25_scenario$mean_percent
print("95% CrI interval:")
paste0("[",bujumbura_25_scenario$lower_95_percent, ", ", bujumbura_25_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
bujumbura_25_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",bujumbura_25_scenario$lower_averted_95_per_dose, ", ", bujumbura_25_scenario$upper_averted_95_per_dose, "]")

```

# Bujumbura - 50,000 doses/ 2,000 doses per day/ SW first
```{r bujumbura scenarios follout 1 all equal, echo=FALSE, warning=FALSE, message=FALSE}
bujumbura_2000_scenario<-filter(big_df_bujumbura_start, 
                             scenario_dose==50000,
                             scenario_doses_per_day_character == "2,000",
                            scenario_priority%in%c("SWs first"),
                            TimeStep==max(big_df_bujumbura_start$TimeStep, na.rm = TRUE), 
                            Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
bujumbura_2000_scenario$mean_averted
print("95% CrI interval:")
paste0("[",bujumbura_2000_scenario$lower_95_averted, ", ", bujumbura_2000_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
bujumbura_2000_scenario$mean_percent
print("95% CrI interval:")
paste0("[",bujumbura_2000_scenario$lower_95_percent, ", ", bujumbura_2000_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
bujumbura_2000_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",bujumbura_2000_scenario$lower_averted_95_per_dose, ", ", bujumbura_2000_scenario$upper_averted_95_per_dose, "]")

```


## Sud Kivu, 2 million doses / 250 rollout / all equal 

```{r sud kivu scenarios rollout 250 all equal, echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_priority%in%c("All equal"),
                          scenario_dose==2000000,
                          scenario_doses_per_day_character == "   250",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")
```
## Sud Kivu, 2 million doses / 20,000 rollout / all equal 

```{r sud kivu scenarios 20000 all equal , echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_priority%in%c("All equal"),
                          scenario_dose==2000000,
                          scenario_doses_per_day_character == "20,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")
```


## Sud Kivu, 2 million doses / 250 rollout / SWs first

```{r sud kivu scenarios rollout 250 SW, echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("K: MVA-BN + fractional + SWs first"),
                          scenario_dose==2000000,
                          scenario_doses_per_day_character == "   250",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")
```

## Sud Kivu, 2 million doses / 20,000 rollout / SWs first 

```{r sud kivu scenarios 20000 SW , echo=FALSE, warning=FALSE, message=FALSE}

sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("K: MVA-BN + fractional + SWs first"),
                          scenario_dose==2000000,
                          scenario_doses_per_day_character == "20,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")
```

## fractional SK 

```{r sud kivu fractional, echo=FALSE, warning=FALSE, message=FALSE}
print("one full dose")
sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("F: MVA-BN"),
                          scenario_dose==500000,
                                              scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")

print("one fractional dose")
sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("I: MVA-BN + fractional"),
                          scenario_dose==500000,
                          scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")
```

## fractional SK 2 million

```{r sud kivu fractional, echo=FALSE, warning=FALSE, message=FALSE}
print("one full dose")
sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("F: MVA-BN"),
                          scenario_dose==2000000,
                                              scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")

print("Mean doses given:")
sudkivu_nopriority_scenario$mean_cumulative_doses
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_cumulative_doses, ", ", sudkivu_nopriority_scenario$upper_95_cumulative_doses, "]")

print("one fractional dose")
sudkivu_nopriority_scenario<-filter(big_df_sudkivu_start, 
                          scenario_labels%in%c("I: MVA-BN + fractional"),
                          scenario_dose==2000000,
                          scenario_doses_per_day_character == " 5,000",
                          TimeStep==max(big_df_sudkivu_start$TimeStep),
                          Category%in%c("cases_inc_cum"))|>top_n(1, mean_averted)

print("Mean cases averted:")
sudkivu_nopriority_scenario$mean_averted
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_averted, ", ", sudkivu_nopriority_scenario$upper_95_averted, "]")

print("Mean percent cases averted:")
sudkivu_nopriority_scenario$mean_percent
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_percent, ", ", sudkivu_nopriority_scenario$upper_95_percent, "]")

print("Mean cases averted per dose:")
sudkivu_nopriority_scenario$mean_averted_per_dose
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_averted_95_per_dose, ", ", sudkivu_nopriority_scenario$upper_averted_95_per_dose, "]")

print("Mean doses given:")
sudkivu_nopriority_scenario$mean_cumulative_doses
print("95% CrI interval:")
paste0("[",sudkivu_nopriority_scenario$lower_95_cumulative_doses, ", ", sudkivu_nopriority_scenario$upper_95_cumulative_doses, "]")
```


## Transmission route percentages

```{r transmission, echo=FALSE, warning=FALSE, message=FALSE}
pmcmc_results_e <- readRDS("inputs/samples_equateur.RDS")

    # unpack results
    pars_unpacked_e <- apply(pmcmc_results_e$pars, 2, pmcmc_results_e$packer$unpack)
    pars_unpacked_s <- apply(pmcmc_results_s$pars, 2, pmcmc_results_s$packer$unpack)
    pars_unpacked_b <- apply(pmcmc_results_b$pars, 2, pmcmc_results_b$packer$unpack)
    
    state_e <- extract_state(pars_unpacked_e, region = "equateur", pmcmc_results=pmcmc_results_e) 
    state_s <- extract_state(pars_unpacked_s, region = "sudkivu", pmcmc_results=pmcmc_results_s) 
    state_b <- extract_state(pars_unpacked_b, region = "burundi", pmcmc_results=pmcmc_results_b) 
       
  
state_tidy <- rbind(state_e, state_s, state_b) |> 
      group_by(region, particle) |> 
      mutate(prop = value / sum(value)) |>
      rowwise() |>
      mutate(region = nms_region[region]) |>
        group_by(state, region) |>
      summarise(median_prop=median(prop), mean_prop = mean(prop),
                lower_prop=quantile(prop, 0.025), upper_prop=quantile(prop, 0.975))
  
 # Equateur zoonotic transmission percentage
  state_tidy|>filter(region=="Equateur", state=="Zoonotic")|>tibble()
  
# Equateur average zoonotic infections 
 daily_zoonotic_equateur<- extract_daily_zoonotic_region(pars_unpacked_e, region = "equateur", both=FALSE)
  print("Avergae zoonotic infections over all age groups:")
 daily_zoonotic_equateur|>filter(!group%in%(c("CSW","ASW","PBS","HCW")))|>summarise(sum=sum(mean))
 
  
```

## All regions - R0 values

```{r R0, echo=FALSE, warning=FALSE, message=FALSE}
    r0_e <- calc_R0(pmcmc_results_e, "equateur", no_historic_vax = TRUE)
    r0_s <- calc_R0(pmcmc_results_s, "sudkivu", no_historic_vax = TRUE)
    r0_b <- calc_R0(pmcmc_results_b, "bujumbura", no_historic_vax = TRUE)
    r0 <-rbind(r0_e|>as.data.frame()|>mutate(region="equateur"), 
               r0_s|>as.data.frame()|>mutate(region="sudkivu"),
               r0_b|>as.data.frame()|>mutate(region="burundi"))|>
      group_by(region)|>
      pivot_longer(names_to = "name", values_to = "value", cols=1:3)
    
#R0 summariers
r0_summary<-r0|>group_by(region, name)|>summarise(mean=mean(value), lower_95=quantile(value, 0.025), upper_95=quantile(value,0.975))
r0_summary
    
```


## CFR - by age groups 

```{r cfr lower percent, echo=FALSE, warning=FALSE, message=FALSE}

# historic clade 1 b
both=FALSE
cfr_prior_summary <- extract_cfr_by_age(pars_unpacked_e, region="equateur", both=both, summarise = FALSE, name = "CFR_0") 
# mean clode 1 over all age groups
print("Mean clade 1 historic over all age groups")
mean(cfr_prior_summary[1:16,1], na.rm=TRUE)

## # percentage lower than historic 

# EQUATEUR
cfr_equateur <- extract_cfr_by_age(pars_unpacked_e, region="equateur", both=both, summarise = FALSE, name = "CFR")[1:16,1:1000]|>tibble()

percent_lower_eq<-(cfr_prior_summary[1:16,1:1000]-cfr_equateur)/cfr_prior_summary[1:16,1:1000]

percent_lower_eq_mean_over_age <- apply(percent_lower_eq, 2, mean)

print("Equateur: % lower than prior")
#mean of means over particles
mean(percent_lower_eq_mean_over_age)
# lower quantile of means over particles
quantile(percent_lower_eq_mean_over_age, 0.025)
# upper quantile of means over particles
quantile(percent_lower_eq_mean_over_age, 0.975)

# SUD KIVU 
cfr_sudkivu <- extract_cfr_by_age(pars_unpacked_s, region="sudkivu", both=both, summarise = FALSE, name = "CFR")[1:16,1:1000]|>tibble()

percent_lower_sk<-(cfr_prior_summary[1:16,1:1000]-cfr_sudkivu)/cfr_prior_summary[1:16,1:1000]

percent_lower_sk_mean_over_age <- apply(percent_lower_sk, 2, mean)

print("Sud Kivu: % lower than prior")
#mean of means over particles
mean(percent_lower_sk_mean_over_age)
# lower quantile of means over particles
quantile(percent_lower_sk_mean_over_age, 0.025)
# upper quantile of means over particles
quantile(percent_lower_sk_mean_over_age, 0.975)

# Summaries by age group
# EQUATEUR
extract_cfr_by_age(pars_unpacked_e, region="equateur", both=both, summarise = TRUE, name = "CFR")|>mutate(region="equateur")
# SUD KIVU
extract_cfr_by_age(pars_unpacked_s, region="sudkivu", both=both, summarise = TRUE, name = "CFR")|>mutate(region="sudkivu")


```



