---
title: "Values for paper"
output:
  pdf_document: default
  html_document: default
date: "2025-06-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

orderly2::orderly_resource("support.R")
source("support.R")
library(tidyverse)
library(patchwork)
library(mpoxseir)
library(ggplot2)

```

```{r,include=FALSE}
# read in data dependencies
pmcmc_results_e <- readRDS("inputs/samples_equateur.RDS")
fitting_data_e <- readRDS("inputs/fitting_data_equateur.RDS")
pmcmc_results_s <- readRDS("inputs/samples_sudkivu.RDS")
fitting_data_s <- readRDS("inputs/fitting_data_sudkivu.RDS")
pmcmc_results_b <- readRDS("inputs/samples_burundi.RDS")
fitting_data_b <- readRDS("inputs/fitting_data_burundi.RDS")

pars_tidy_e <- tidy_pars(pmcmc_results_e)
pars_tidy_s <- tidy_pars(pmcmc_results_s)
pars_tidy_b <- tidy_pars(pmcmc_results_b)
  
pars_tidy <- rbind(pars_tidy_e |> mutate(region="equateur"),
                   pars_tidy_s |> mutate(region="sudkivu"),
                   pars_tidy_b |> mutate(region="burundi"))


pars_summary <- pars_tidy %>% group_by(name, region) %>%
  summarise(mean = round(mean(value,na.rm=TRUE),2),
            lower = round(quantile(value,0.025,na.rm = TRUE),2),
            upper = round(quantile(value,0.975,na.rm = TRUE),2)) 


pars_summary_SW <- pars_tidy %>% filter(name=="prop_SW") %>% 
  mutate(value = value*100) %>% group_by(region) %>%
    summarise(mean = round(mean(value,na.rm=TRUE),2),
            lower = round(quantile(value,0.025,na.rm = TRUE),2),
            upper = round(quantile(value,0.975,na.rm = TRUE),2)) 

ascert <- read.csv("outputs/ascertainment_separate.csv") %>%
  mutate(equateur = round(equateur,2),
         sudkivu = round(sudkivu,2),
         burundi = round(burundi,2))


prop_trans <- read.csv("outputs/prop_transmission_with_uncertainty.csv") %>%
  filter(state!="Nosocomial")

zoonotic <- read.csv("outputs/zoonotic_eq.csv") %>%
  mutate(mean = round(mean,2),
        q2.5 = round(q2.5,2),
         q97.5 = round(q97.5,2))

cfr <- read.csv("outputs/cfr.csv") %>%
  mutate(mean = round(mean*100,1),
         q2.5 = round(q2.5*100,1),
         q97.5 = round(q97.5*100,1)) %>%
  select(region,group,mean,q2.5,q97.5)


```



# Case ascertainment

Make sure you have loaded the latest fits!

## Equateur
```{r, include=TRUE}
pars_summary %>% filter(region=="equateur",name %in% c("phi_05_14","phi_15_plus"))
```
# percentage of posterior parameter sets where phi_15_plus>phi_05_14
```{r, include=TRUE}
phi_15_plus_post_e <- pars_tidy %>% filter(region=="equateur",name=="phi_15_plus")
phi_05_14_post_e <- pars_tidy %>% filter(region=="equateur",name=="phi_05_14")

# Percentage where
# phi_15_plus > phi_05_14
sum(phi_15_plus_post_e$value > phi_05_14_post_e$value)/nrow(phi_15_plus_post_e)

```

## Sud Kivu
```{r, include=TRUE}
pars_summary %>% filter(region=="sudkivu",name %in% c("phi_05_14","phi_15_plus"))
```
# percentage of posterior parameter sets where phi_15_plus>phi_05_14
```{r, include=TRUE}
phi_15_plus_post_s <- pars_tidy %>% filter(region=="sudkivu",name=="phi_15_plus")
phi_05_14_post_s <- pars_tidy %>% filter(region=="sudkivu",name=="phi_05_14")

# Percentage of posterior samples where
# phi_15_plus > phi_05_14
sum(phi_15_plus_post_s$value > phi_05_14_post_s$value)/nrow(phi_15_plus_post_s)

```

## Bujumbura
```{r, include=TRUE}
pars_summary %>% filter(region=="burundi",name %in% c("phi_05_14","phi_15_plus"))
```
# percentage of posterior parameter sets where phi_15_plus>phi_05_14
```{r, include=TRUE}
phi_15_plus_post_b <- pars_tidy %>% filter(region=="burundi",name=="phi_15_plus")
phi_05_14_post_b <- pars_tidy %>% filter(region=="burundi",name=="phi_05_14")

# Percentage of posterior samples where
# phi_15_plus > phi_05_14
sum(phi_15_plus_post_b$value > phi_05_14_post_b$value)/nrow(phi_15_plus_post_b)

```

## all regions 
# percentage of posterior parameter sets where phi_15_plus>phi_05_14
```{r, include=TRUE}
phi_15_plus_post <- pars_tidy %>% filter(name=="phi_15_plus")
phi_05_14_post <- pars_tidy %>% filter(name=="phi_05_14")

# Percentage of posterior samples where
# phi_15_plus > phi_05_14
sum(phi_15_plus_post$value > phi_05_14_post$value)/nrow(phi_15_plus_post)

```

## overall ascertainment
```{r, include=TRUE}
ascert %>% t() %>% data.frame()
```



# SW prop
## Equateur
```{r, include=TRUE}
pars_summary %>% filter(region=="equateur",name=="prop_SW")
```

## Sud Kivu
```{r, include=TRUE}
pars_summary %>% filter(region=="sudkivu",name=="prop_SW")
```

## Bujumbura
```{r, include=TRUE}
pars_summary %>% filter(region=="burundi",name=="prop_SW")
```



# Transmissibility

## Equateur
```{r, include=TRUE}
pars_summary %>% filter(region=="equateur",name %in% c("R0_hh","R0_sw_st"))
```

## Sud Kivu
```{r, include=TRUE}
pars_summary %>% filter(region=="sudkivu",name %in% c("R0_hh","R0_sw_st"))
```

## Bujumbura
```{r, include=TRUE}
pars_summary %>% filter(region=="burundi",name %in% c("R0_hh","R0_sw_st"))
```


# Proportion by transmission route

## Equateur
```{r,include = TRUE}
prop_trans %>% filter(region=="equateur")
```

## Sud Kivu
```{r,include = TRUE}
prop_trans %>% filter(region=="sudkivu")
```

## Bujumbura
```{r,include = TRUE}
prop_trans %>% filter(region=="burundi")
```


# Zoonotic spillover (Equateur only)
```{r, include=TRUE}
zoonotic %>% dplyr::select(group,mean,q2.5,q97.5)

```

# Severity

## Prior
```{r, include=TRUE}
cfr %>% filter(region == "prior")

```


## Equateur
```{r, include=TRUE}
cfr %>% filter(region == "equateur")

```

## Sud Kivu
```{r, include=TRUE}
cfr %>% filter(region == "sudkivu")

```






